### 2025-02-17 tfp2025 3/src/sections/1-introduction.tex
work

\jr{Elliot has kicked off this effort...}
Recent work by Elliot uses interactive theorem provers to state simple specifications of languages and that proofs of desirable properties of these language specifications transfer easily to their parsers \cite{conal-languages}. Unfortunately, this work only considers regular languages which are not powerful enough to describe practical programming languages.

@@

In this paper, we formalize context-free languages and show how to parse them, extending Elliot’s type theoretic approach to language specfication.  One of the main challenges is that the recursive nature of context-free languages does not map directly onto interactive theorem provers as they do not support general recursion (for good reasons). We encode context-free languages as fixed points of functors (initial algebras).

@@

We make the following concrete contributions:
\begin{itemize}
\item We extend Elliot's type theoretic formalization of regular languages to context-free languages.
\end{itemize}

@@

% In section 2:
% * Could: "This is a background section"
% * We recall Elliot's ...
% * To make it easier to add fixed points in the next section

>>>>

\jr{Elliott has kicked off this effort...}
Recent work by Elliott uses interactive theorem provers to state simple specifications of languages and that proofs of desirable properties of these language specifications transfer easily to their parsers \cite{conal-languages}. Unfortunately, this work only considers regular languages which are not powerful enough to describe practical programming languages.

@@

In this paper, we formalize context-free languages and show how to parse them, extending Elliott’s type theoretic approach to language specfication.  One of the main challenges is that the recursive nature of context-free languages does not map directly onto interactive theorem provers as they do not support general recursion (for good reasons). We encode context-free languages as fixed points of functors (initial algebras).

@@

We make the following concrete contributions:
\begin{itemize}
\item We extend Elliott's type theoretic formalization of regular languages to context-free languages.
\end{itemize}

@@

% In section 2:
% * Could: "This is a background section"
% * We recall Elliott's ...
% * To make it easier to add fixed points in the next section

### 2025-02-17 tfp2025 3/src/sections/4-discussion.tex
work

\paragraph{Simplicity}
One of the main contributions of Elliot's type theoretic formalization of languages~\cite{conal-languages} is its simplicity of implementation and proof. To be able to extend his approach to context-free languages we have had to introduce some complications.
\jr{TODO: finish this paragraph}
% Most notably, we use fuel to define the semantics of our grammars. We have explored other approaches such as using guarded type theory, but we did not manage to significantly simplify our formalization. Furtheremore, we expect that many proofs remain simple despite our fuel-based approach.
\medbreak

>>>>

\paragraph{Simplicity}
One of the main contributions of Elliott's type theoretic formalization of languages~\cite{conal-languages} is its simplicity of implementation and proof. To be able to extend his approach to context-free languages we have had to introduce some complications.
\jr{TODO: finish this paragraph}
% Most notably, we use fuel to define the semantics of our grammars. We have explored other approaches such as using guarded type theory, but we did not manage to significantly simplify our formalization. Furtheremore, we expect that many proofs remain simple despite our fuel-based approach.
\medbreak
